### 2015-05-14 evaluation.tex
fixes

Using the race-freedom guarantees from \whoop, we managed to significantly accelerate \corral in most of our benchmarks; the best results were achieved using \yieldmr. Figure~\ref{fig:plot} shows that most speedups using \yieldmr are in the range of 1.5--10$\times$; while in ssu100, and pc8736x\_gpio respectively, we achieved a speedup of 12$\times$, and 20$\times$ respectively, using a csb of 9. We notice that a higher csb typically results into greater speedups, when exploiting \whoop. This is expected, as a higher csb directly translates into a larger sequentialized program, and thus \whoop has more opportunities to reduce the sequentialization.
%
However, if \whoop fails to verify any race-related properties of a driver, it can slow down \corral. We noticed this in the sx8 driver, where \whoop does not verify any pairs, causing unnecessary overhead. Although \whoop verified 46 out of 47 memory regions, it still fails to speedup \corral using \yieldmr. \corral checks the only two pairs associated with sx8 quite quickly (21.4 seconds with csb of 9), so the overhead of running \whoop outweighs the benefits of fine-grained instrumentation.

>>>>

Using the race-freedom guarantees from \whoop, we managed to significantly accelerate \corral in most of our benchmarks; the best results were achieved using \yieldmr. Figure~\ref{fig:plot} shows that most speedups using \yieldmr are between 1.5$\times$ and 10$\times$; while in ssu100, and pc8736x\_gpio respectively, we achieved a speedup of 12$\times$, and 20$\times$ respectively, using a csb of 9. We noticed that a higher csb typically results into greater speedups, when exploiting \whoop. This is expected, as a higher csb directly translates into a larger sequentialized program, and thus \whoop has more opportunities to reduce the sequentialization.
%
However, if \whoop fails to verify any race-related properties of a driver, it can slow down \corral. We noticed this in the sx8 driver, where \whoop does not verify any pairs, causing unnecessary overhead. Although \whoop verified 46 out of 47 memory regions of sx8, it still failed to speedup \corral using \yieldmr. \corral checks the only two pairs associated with sx8 quite quickly (21.4 seconds with csb of 9), so the overhead of running \whoop outweighs the benefits of fine-grained instrumentation.
